---
title: "ch1_tidy_text_format"
output: html_document
---
The Tidy Text Format

Tidy text format is a table with one-token-per-row
```{r}
#Introduction to the unnest_tokens function
text <- c("Because I could not stop for Death -",
          "He kindly stopped for me -",
          "The Carriage held but just Ourselves -",
          "and Immortality")
text #appears as a typical character vector

#Put nto a dataframe to turn into a tidy text dataset
library(dplyr)
text_df <- data_frame(line = 1:4, text = text)
text_df #appears as a tibble - modern class of df in R -> we like tibbles

#We want to convert to one-token-per-document-per-row
library(tidytext)
text_df %>% 
  unnest_tokens(word, text) #used text instead of text_df
  #line number is retained
  #removed punctation
  #converts to lowercase
#these make it easy to manipulate, process, and visualize the text
```
Looking at the work of Jane Austen
```{r jane}
library(janeaustenr)
library(dplyr)
library(stringr)

original_books <- austen_books() %>% #takes all the austen books
  group_by(book) %>% #groups by book title
  mutate(linenumber = row_number(),
         chapter = cumsum(str_detect(text, regex("^chapter [\\divxlc]",
                                                 ignore_case = TRUE)))) %>%
  ungroup()
original_books

library(tidytext)
tidy_books <- original_books %>%
  unnest_tokens(word, text) #does magic
tidy_books 

#stop_words is a dataset of words not useful for analysis such as 'the', 'of', and 'to'
data(stop_words)
tidy_books <- tidy_books %>% anti_join(stop_words)

#count() allows us to find the most comomon words in ALL of the books
tidy_books %>% count(word, sort = TRUE)


#plotting common words from austen books with ggplot2
library(ggplot2)

tidy_books %>% 
  count(word, sort = TRUE) %>%
  filter(n > 600) %>% #greater than 600 iterations to limit plot
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()
```
Guternbergr Package provides access to Project Gutenberg.
Includes tools for downloading and complete dataset of metadata books
```{r}
library(gutenbergr)

#downloading works of HG wells using ID numbers for each novel 
#the time machine, the war of the worlds, the invisible man, the island of doctor moreau
hgwells <- gutenberg_download(c(35, 36, 5230, 159))

tidy_hgwells <- hgwells %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words)

tidy_hgwells %>% count(word, sort=TRUE)

#downloading works of bronte sisters using ID
bronte <- gutenberg_download(c(1260, 768, 969, 9182, 767))

tidy_bronte <- bronte %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words)

tidy_bronte %>% count(word, sort= TRUE)
```
Calculate word frequency for works of Austen, Bronte, and HGWells
```{r}
library(tidyr)

frequency <- bind_rows(mutate(tidy_bronte, author = "Brontë Sisters"),
                       mutate(tidy_hgwells, author = "H.G. Wells"),
                       mutate(tidy_books, author = "Jane Austen")) %>%
  mutate(word = str_extract(word, "[a-z']+")) %>% #ensures that _any_ is not separate from any
  count(author, word) %>%
  group_by(author) %>%
  mutate(proportion = n/sum(n)) %>%
  select(-n) %>%
  spread(author, proportion) %>%
  gather(author, proportion, `Brontë Sisters`:`H.G. Wells`)

library(scales)

ggplot(frequency, aes(x=proportion, y=`Jane Austen`, color=abs(`Jane Austen` - proportion))) +
  geom_abline(color = "gray20", lty=2) +
  geom_jitter(alpha  = 0.1, size = 2.5, width = 0.3, height = 0.3) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  scale_color_gradient(limits = c(0, 0.001), low = "darkslategray4", high = "gray75") +
  facet_wrap(~author, ncol = 2) +
  theme(legend.position = "none") + 
  labs(y = "Jane Austen", x = NULL)
#words closest to the line have similar frequencies in both sets of text 
```
Using a correlation test to look at correlation between word frequencies.
```{r}
#Correlation between Brontë and Austen
cor.test(data = frequency[frequency$author == "Brontë Sisters",], ~ proportion + `Jane Austen`)

#Correlation between Wells and Austen
cor.test(data = frequency[frequency$author == "H.G. Wells",], ~ proportion + `Jane Austen`)
```